Icicle: write once, run once

### 2016-05-15 2016fhpc/section/04-Benchmarks.tex
more bench

We are using Icicle in production, over medium-sized datasets that fit on a single disk.

@@

>>>>

We are currently using Icicle in production, over medium-sized datasets that fit on a single disk.
Initial results have been very promising, and we are currently working towards a distributed implementation for larger datasets.

@@

It is also important to note that, as a very constrained streaming language, memory usage of Icicle queries is more or less constant in the input size, and runtime is linear.
This is very important, as new data is received regularly and the input size grows.
This does not appear to be the case with the R script, which continually requires larger computers with more memory, in order to finish in a reasonable time.
One of the benefits of Icicle is allowing data scientists to focus on queries, without having to worry about performance.
